The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2018-12-03 article.tex
Add hypothesis 7

>>>>

\item We have the hypothesis, H7, 
that there is no difference in inference errors if the MBD process
generates many species in many modest MB events or few intense MB events.

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{fig_h_7.png}
  \caption{
    Hypothesis 7: there is no difference in inference errors if the MBD process
    generates many species in many modest MB events or few intense MB events
  }
  \label{fig_h_7}
\end{figure}
